\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts,amssymb,amsthm} % Math packages
\usepackage[mathscr]{euscript}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage[mathscr]{euscript}
\let\euscr\mathscr \let\mathscr\relax% just so we can load this and rsfs
\usepackage[scr]{rsfso}
\usepackage{pifont}
\usepackage{geometry} % Adjust page margins
\usepackage{titlesec} % Adjust section and subsection formatting
\geometry{a4paper, left=1in, right=1in, top=1in, bottom=1in}

\title{
  \textbf{CS-225: Discrete Structures in CS} \\
  Assignment 7 Part 1
  }
\author{Noah Hinojos}
\date{\today}

\titleformat*{\subsection}{\normalsize\bfseries}

\begin{document}
\maketitle
\subsection*{What stood out to you as the most important things you learned about computer programming this quarter? Why do you think they're important?}
What stood out to me the most was the importance of syntax and formality when writing code. I see the value of consistency, it makes the code readable and easier to understand.
\subsection*{What topics do you still find confusing? What can you do to get a better grasp on them?}
There really isn't anything I find still confusing sinceI have pretty extensive knowledge of Python coming into this course.
\subsection*{What did you learn this quarter about how taking online courses works for you?}
I learned how to manage my time more effectively, yet also the difficulty of overcoming certain learning objectives with my classmates.
\subsection*{How did you use the Exploration and the videos provided? What techniques helped you learn better and when they didn't help you, what did you do?}
No I did not. Again, I had quite extensive knowledge of Python coming into this course.
\subsection*{How can you generalize your experience in this course in a way that will help you in future courses?}
The course works well when you have an established weekly routine, as would all courses I imagine. 
\subsection*{How has this course helped crystallize your ideas about what a career that involves computer programming might be like?}
There isn't really much I can say on this. I don't know. Perhaps it showed me the true challenge when working with others on programming.

\end{document}